CF Registry Analysis - ROC

### 2025-12-23 Christine Chan/CF Registry/cf_registry_ROC_analysis.qmd
a bunch of updates for Christine

@@

```{r}
roc_df |>
  select(`OGTT 2-hour`, Gender, MutClass, hgba1c) |>
  filter(`OGTT 2-hour` != ">=200") |>
  mutate(`OGTT 2-hour` = droplevels(`OGTT 2-hour`)) |>
  tbl_summary(
    by = `OGTT 2-hour`,
    missing_text = "Missing",
    type = list(all_continuous() ~ "continuous2"),
    statistic = list(
      all_continuous() ~
        c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}")
    ),
    label = list(
      hgba1c = "HbA1c",
      Hispanicrace = "Hispanic",
      MutClass = "Mutation Class",
      reviewyear = "Year",
      Age_YrEnd = "Age at Year End"
    )
  ) |>
  add_overall() |>
  add_p(
    test = list(reviewyear = "fisher.test"),
    test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
  ) |>
  separate_p_footnotes() |>
  as_gt()
```

@@

```{r}
roc_df |>
  select(`OGTT 2-hour`, Gender, MutClass, hgba1c) |>
  filter(`OGTT 2-hour` != "<140") |>
  mutate(`OGTT 2-hour` = droplevels(`OGTT 2-hour`)) |>
  tbl_summary(
    by = `OGTT 2-hour`,
    missing_text = "Missing",
    type = list(all_continuous() ~ "continuous2"),
    statistic = list(
      all_continuous() ~
        c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}")
    ),
    label = list(
      hgba1c = "HbA1c",
      Hispanicrace = "Hispanic",
      MutClass = "Mutation Class",
      reviewyear = "Year",
      Age_YrEnd = "Age at Year End"
    )
  ) |>
  add_overall() |>
  add_p(
    test = list(reviewyear = "fisher.test"),
    test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
  ) |>
  separate_p_footnotes() |>
  as_gt()
```

@@

```{r}
roc_df |>
  select(`OGTT 2-hour`, Gender, MutClass, hgba1c) |>
  filter(`OGTT 2-hour` != "[140,200)") |>
  mutate(`OGTT 2-hour` = droplevels(`OGTT 2-hour`)) |>
  tbl_summary(
    by = `OGTT 2-hour`,
    missing_text = "Missing",
    type = list(all_continuous() ~ "continuous2"),
    statistic = list(
      all_continuous() ~
        c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}")
    ),
    label = list(
      hgba1c = "HbA1c",
      Hispanicrace = "Hispanic",
      MutClass = "Mutation Class",
      reviewyear = "Year",
      Age_YrEnd = "Age at Year End"
    )
  ) |>
  add_overall() |>
  add_p(
    test = list(reviewyear = "fisher.test"),
    test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
  ) |>
  separate_p_footnotes() |>
  as_gt()
```

>>>>

P values below are FDR-adjusted for multiple comparisons.

@@

```{r}
roc_df |>
  select(-eDWID) |>
  filter(`OGTT 2-hour` != ">=200") |>
  mutate(`OGTT 2-hour` = droplevels(`OGTT 2-hour`)) |>
  tbl_summary(
    by = `OGTT 2-hour`,
    missing_text = "Missing",
    type = list(
      reviewyear ~ "categorical",
      all_continuous() ~ "continuous2"
    ),
    statistic = list(
      all_continuous() ~
        c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}")
    ),
    label = list(
      hgba1c = "HbA1c",
      Hispanicrace = "Hispanic",
      MutClass = "Mutation Class",
      reviewyear = "Year",
      Age_YrEnd = "Age at Year End"
    )
  ) |>
  add_overall() |>
  add_p(
    test = list(reviewyear = "fisher.test"),
    test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
  ) |>
  add_q() |>
  separate_p_footnotes() |>
  modify_column_hide(p.value) |>
  as_gt()
```

@@

```{r}
roc_df |>
  select(-eDWID) |>
  filter(`OGTT 2-hour` != "<140") |>
  mutate(`OGTT 2-hour` = droplevels(`OGTT 2-hour`)) |>
  tbl_summary(
    by = `OGTT 2-hour`,
    missing_text = "Missing",
    type = list(
      reviewyear ~ "categorical",
      all_continuous() ~ "continuous2"
    ),
    statistic = list(
      all_continuous() ~
        c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}")
    ),
    label = list(
      hgba1c = "HbA1c",
      Hispanicrace = "Hispanic",
      MutClass = "Mutation Class",
      reviewyear = "Year",
      Age_YrEnd = "Age at Year End"
    )
  ) |>
  add_overall() |>
  add_p(
    test = list(reviewyear = "fisher.test"),
    test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
  ) |>
  add_q() |>
  separate_p_footnotes() |>
  modify_column_hide(p.value) |>
  as_gt()
```

@@

```{r}
roc_df |>
  select(-eDWID) |>
  filter(`OGTT 2-hour` != "[140,200)") |>
  mutate(`OGTT 2-hour` = droplevels(`OGTT 2-hour`)) |>
  tbl_summary(
    by = `OGTT 2-hour`,
    missing_text = "Missing",
    type = list(
      reviewyear ~ "categorical",
      all_continuous() ~ "continuous2"
    ),
    statistic = list(
      all_continuous() ~
        c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}")
    ),
    label = list(
      hgba1c = "HbA1c",
      Hispanicrace = "Hispanic",
      MutClass = "Mutation Class",
      reviewyear = "Year",
      Age_YrEnd = "Age at Year End"
    )
  ) |>
  add_overall() |>
  add_p(
    test = list(reviewyear = "fisher.test"),
    test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
  ) |>
  add_q() |>
  separate_p_footnotes() |>
  modify_column_hide(p.value) |>
  as_gt()
```
